01_limma_voom

### 2019-03-19 scripts/01_limma_all.Rmd
now with short labels

levels(colData$sex)
col.sex <- c("#5ab4ac","#d8b365")[colData$sex]
plotMDS(parentalobject,col=col.sex)
legend("bottomright",fill=c("#5ab4ac","#d8b365"),legend=levels(colData$sex))
title("Colored by Sex")
```

>>>>

levels(colData$sex)
col.sex <- c("#5ab4ac","#d8b365")[colData$sex]
plotMDS(parentalobject,col=col.sex)
legend("bottomright",fill=c("#5ab4ac","#d8b365"),legend=levels(colData$sex))
title("Colored by Sex")
```
```{r plotMDS-colorshape}
colData$sexTissue <- paste(colData$sex, colData$tissue, sep = "_")

plotMDS(parentalobject,col=col.treatment, labels = colData$sexTissue)
legend("bottomright",fill=c("#a6cee3", "#1f78b4", "#b2df8a", "#33a02c", "#fb9a99", "#e31a1c", "#fdbf6f", "#ff7f00", "#cab2d6"),legend=levels(colData$treatment))
title("Colored by Treatment")
```
